\Large \bf Security Audit of Safeplug ``Tor in a Box''

### 2014-07-01 foci/paper.tex
more changes to FOCI paper

\subsection{Latency}
If the latency of web requests using the Safeplug is noticeably longer than that of normal Internet use, users may be deterred from using the device.  Similarly, if turning Tor on, but not ad-blocking, adds a significant time delay, the user may only turn on the ad-blocking feature (without Tor).  We recorded the time for a web request on a variety of settings, shown in Figure~\ref{fig:latency2}.

%\begin{itemize} \setlength{\itemsep}{.2mm}
%\item Plain Firefox (no use of the Safeplug device)
%\item Firefox, no Tor, no ad-blocking (traffic running through the Safeplug device)
%\item Firefox, Tor, no ad-blocking
%\item Firefox, Tor, ad-blocking
%\item Firefox, no Tor, ad-blocking
%\item Tor Browser Bundle with Safeplug (all settings off)
%\item Tor Browser Bundle
%\end{itemize}

For each of the settings, we took 20 measurements; Figure~\ref{fig:latency2} shows the average time of a web request on each of the specified settings for three different web pages.  When taking these measurements, we loaded the page, but did not scroll; in many cases more objects are loaded when scrolling down a page.  The differences between web pages can most likely be attributed to the amount of advertisements and content running in plugins (such as video) on the web page.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{latencygraph}
  \caption{Latency of web requests.}
  \label{fig:latency2}
\end{figure}

@@

It is clear that the Tor Browser Bundle had the fewest privacy implications in most categories. The one category where Privoxy performed better than the Tor Browser Bundle is in the number of JavaScript objects received from third parties; this can be attributed to the fact that our measurements were taken using the default settings for the Tor Browser Bundle, which allows JavaScript (NoScript is disabled)~\cite{torproject}.  This is explained on the Tor Project's website; they explain that disabling JavaScript causes some web pages to break, making the browser less user-friendly.  The user has the option to enable JavaScript by simply clicking a button.  This shows that the Tor Browser is a less expensive alternative to the Safeplug, and provides more privacy protections.

@@

>>>>

\subsection{Latency}
If the latency of web requests using the Safeplug is noticeably longer than that of normal Internet use, users may be deterred from using the device.  Similarly, if turning Tor on, but not ad-blocking, adds a significant time delay, the user may only turn on the ad-blocking feature (without Tor).  We recorded the time for a web request on the following settings:

\begin{itemize} %\setlength{\itemsep}{2mm}
\item Plain Firefox (no use of the Safeplug device)
\item Firefox, no Tor, no ad-blocking (traffic running through the Safeplug device)
\item Firefox, Tor, no ad-blocking
\item Firefox, Tor, ad-blocking
\item Firefox, no Tor, ad-blocking
\item Tor Browser Bundle with Safeplug (all settings off)
\item Tor Browser Bundle
\end{itemize}

For each of the settings, we took 20 measurements [TODO: explain why only 20 measurements]; Figure~\ref{fig:latency2} shows the average time of a web request on each of the specified settings for three different web pages.  When taking these measurements, we loaded the page, but did not scroll; in many cases more objects are loaded when scrolling down a page.  The differences between web pages can most likely be attributed to the amount of advertisements and content running in plugins (such as video) on the web page.

\begin{figure*}
  \centering
  \includegraphics[width=0.5\textwidth]{latencygraph}
  \caption{Latency of web requests.}
  \label{fig:latency2}
\end{figure*}

TODO: talk about variation within specific categories for each site.

The average web request time for accessing \url{www.washingtonpost.com} is greatest on the same settings that the average web request time for \url{www.google.com} is the least. This setting did not include ad-blocking, and therefore \url{www.washingtonpost.com} had to render each ad (which it requested through Tor); \url{www.google.com} does not have any ads.

The latency of using the Safeplug with Firefox, Tor, and ad-blocking is comparable to that of using the Tor Browser Bundle.  For all three web pages, the Tor Browser Bundle had slightly lower latency; the Tor Browser Bundle blocks scripts, and for web pages such as \url{www.coca-cola.com}, this provides a significant latency decrease.  This, in conjunction with the fact that the Tor Browser Bundle is free and is issued directly from The Tor Project, shows a convincing argument to use the Tor Browser Bundle in place of the Safeplug.

TODO: mention caveat that we might just be seeing variation in circuit performance because close timing of fetches.

@@

It is clear that the Tor Browser Bundle had the fewest privacy implications in most categories. The one category where Privoxy performed better than the Tor Browser Bundle is in the number of JavaScript objects received from third parties; this can be attributed to the fact that our measurements were taken using the default settings for the Tor Browser Bundle, which allows JavaScript~\cite{torproject}.  This is explained on the Tor Project's website; they explain that disabling JavaScript causes some web pages to break, making the browser less user-friendly.  The user has the option to disable JavaScript by simply clicking a button.  This shows that the Tor Browser is a less expensive alternative to the Safeplug, and provides more privacy protections.

@@

\section{Future Work}
TODO: Talk about performance measurements - specifically to do more than 20 fetches and spread the fetches out over time to ensure different Tor circuits.  Talk about privoxy vs tbb measurements - improvements.
